A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
K2 is not a AAS-approved facility keyword. We could petition for it to be, but it is not currently. See http://aas.org/aastex/facility-keywords
What else can we use this for?

@@

{\it Facilities:} \facility{Kepler}, \facility{K2}

>>>>

Additionally, while we apply this systematics model simultaneously with a 
transiting planet model to search for planet candidates, this scheme is 
not restricted to planet searches.
Any astrophysical event that could be observed in the \KT\ data could be 
searched for in the same way. 
By modeling a set of ELCs with any arbitrary data model, events in the \KT\
data that appear similar to that data model could be identified. 
Such a technique may be useful in searching for astrophysical events such as
ellipsoidal variations induced by orbiting companions,
stellar activity,
microlensing events, especially in the upcoming Campaign 9,
or
active galactic nuclei variability.

@@

{\it Facilities:} \facility{Kepler}
